Privacy-Respecting Type Error Telemetry at Scale

### 2023-10-14 programming23/paper.tex
prio + poplar

>>>>

Prio and Poplar demonstrate a telemetry method to compute public aggregates
over private data using a middle layer of
servers~\cite{cb-nsdi-2017,bbcgi-sp-2021}.
Clients can depend on strong privacy guarantees even if other clients and some
servers (but not all) are malicious.
The design has been deployed in Mozilla Firefox to monitor blocklist
usage~\cite{mozilla-prio}.
Luau telemetry might benefit from a redesign to use middle-layer servers,
though it is unclear what data from type analysis would support meaningful
aggregates.
%% In particular, the data would still need to be relatively small to trasmit.
